Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-06 ms.tex
conclusions 4

  \item Low mass AGN have growth times comparable to the Hubble time (\citet{Heckman+04}).  Our results show that this would require accretion rates which are not consistent with steady-state, thermally stable accretion of stellar wind material.  Low mass black hole growth must instead be driven by an external supply of gas.
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they agree to
    within a factor of order unity. This is because in our model the
    accretion rate is determined by the flow properties at the
    stagnation radius, $\rs$, which is within a factor of a few of the
    Bondi radius $\rb$. Thus, use of the Bondi formula is a
    good approximation.
    \end{enumerate}

>>>>

  \item Low mass black holes grow in the low redshift universe over timescales comparable to the Hubble time (\citet{Heckman+04}).  This requires accretion rates which are too high to be consistent with the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).  Low-$M_{\bullet}$ growth and AGN activity must instead be driven by gas supplies external to the nuclear region.

%  \item Our calculation of $\Mdot$ agrees well with the one calculated from the Bondi formula. We find that they agree to
 %   within a factor of order unity. This is because in our model the
  %  accretion rate is determined by the flow properties at the
   % stagnation radius, $\rs$, which is within a factor of a few of the
    %Bondi radius $\rb$. Thus, use of the Bondi formula is a
    %good approximation.

\end{enumerate}
